\documentclass[twoside,11pt]{report}

% Any additional packages needed should be included after AMP-report-style.
% Note that AMP-report-style.sty includes epsfig, amssymb, natbib and graphicx,
% and defines many common macros, such as 'proof' and 'example'.
%
% It also sets the bibliographystyle to plainnat; for more information on
% natbib citation styles, see the natbib documentation.

% Available options for package AMP-report-style are:
%
%   - abbrvbib : use abbrvnat for the bibliography style
%   - nohyperref : do not load the hyperref package
%   - preprint : remove JMLR specific information from the template,
%         useful for example for posting to preprint servers.
%
% Example of using the package with custom options:
%

\usepackage{AMP-report-style}

% Definitions of handy macros can go here

\usepackage{lastpage}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{subcaption}
\newcommand{\comment}[1]{\textcolor{red}{#1}}

\jmlrheading{}{}{1-\pageref{LastPage}}{Dec. 5, 2025}{}{}{}

% Short headings should be running head and authors last names

% \ShortHeadings{}{One and Two}
\firstpageno{1}

\begin{document}

\title{Formal Safety Analysis of Multi-Robot Behavior Trees}

\author{\name Stefan Caldararu \email stefan.caldararu@colorado.edu\\
        \addr Department of Computer Science\\
        University of Colorado Boulder
        \AND
        \name Zack Allen \email zack.allen@colorado.edu\\ 
        \addr Department of Robotics\\
        University of Colorado Boulder      
}

\editor{}

\maketitle

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
    Behavior Trees are structures commonly used in robotics breaking down complicated tasks into subtasks and organizing them into easily readable and programable structures. However, Behavior Trees provide limited support for formal safety analysis, and the challenge grows significantly when multiple robots operate in parallel. In this paper, we formalize a conversion process between Behavior Trees and Finite State Machines. We apply this conversion process to two separate Behavior Trees used in an electric vehicle battery disassembly task involving a humanoid robot and a 6DOF robotic arm working in parallel. After the conversion, we combine the two constructed Finite State Machines by taking the product space. This process allows for a formal safety checking using reachability on selected unsafe states in the product Finite State Machines. This demonstrates a specific application for this generalizable method which can be used to verify and/or modify the design of the original Behavior Trees.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\input{intro}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem Description}
\input{problem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}
\input{method}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results} 
\input{results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion} 
\input{conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip 0.2in
\bibliography{main.bib}

\end{document}
